A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-05-20 manuscript.Rmd
fix typo

```{r echo=FALSE}
```{r}
# define a print method for objects of the class data.frame
knit_print.data.frame = function(x, ...) {
  res = paste(c('', '', kable(x)), collapse = '\n')
  asis_output(res)
}
# register the method
registerS3method("knit_print", "data.frame", knit_print.data.frame)
```

>>>>

```{r echo=FALSE}
# define a print method for objects of the class data.frame
knit_print.data.frame = function(x, ...) {
  res = paste(c('', '', kable(x)), collapse = '\n')
  asis_output(res)
}
# register the method
registerS3method("knit_print", "data.frame", knit_print.data.frame)
```
